---
title: "CSV, GMD-Biplot, and DirichletMultinomial"
author: "Stephen Johnson"
date: "3/31/2020"
output: html_document
---

```{r setup, include=FALSE}
devtools::load_all("./", TRUE)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Compositional Variable Selection using the CVS package

Compositional variable selection is performed using the `cvs` function in `predictive_modeling.R`. The function is implemented as described in [Lin et al., 2014](https://doi.org/10.1093/biomet/asu031). The link to the package itself is only available [here](http://www.math.pku.edu.cn/teachers/linw/software/cvs.zip), but the files bundled with `stromboli` should work on OS X / *nix-based systems. If using Windows, please use the author's link. 

We've adapted the example code from `bmi.R` included with `cvs` to work with `stromboli` data objects and tried to make it as simple as possible to use. Simply call `cvs()` with your data object, variable of interest, and taxonomic level, and you will get the selected variables (as a table, and as a plot) 

```{r}
data("Constipation")

#Note this can take a few minutes to run! Use a higher boostrap.num than 10!
cvs_results <- cvs(data.obj, grp.name="BMI", level="Genus", bootstrap.num=10)
cvs_results$df

cvs_results$taxa_plot

cvs_results$fitted_plot


```

## Subtype modeling using the DirichletMultinomial package

Performing subtype analysis using `stromboli` is also quite simple using the `dirichlet_multinomial` function. Our implementation was adapted from the [`microbiome` package tutorial](https://microbiome.github.io/tutorials/DMM.html) to work with `stromboli` data objects. 

```{r}
data("Constipation")

DM_results <- dirichlet_multinomial(data.obj, components=3, level="Genus")
DM_results[1]
DM_results[2]
DM_results[3]

```

## Beta diversity analysis using the GMD-biplot

In `stromboli` we also include a wrapper function for the GMD Biplot as included in the `GMDecomp` package and described in [Wang et al, 2019](https://msystems.asm.org/content/4/6/e00504-19). Our `gmd_biplot` function wraps around the `GMDecomp::GMD()` function and takes care of all the matrix operations described in the paper but not done by that function. `gmd_biplot` returns a screeplot in addition to the actual GMD biplot.  

```{r}
data("Constipation")
gmd_plot <- gmd_biplot(data.obj, dist.obj, grp.name="Visit", components=4)

gmd_plot$screeplot

gmd_plot$biplot
```
