---
title: "Performing basic summary statistics with stromboli"
author: "Stephen Johnson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
devtools::load_all("./", TRUE)
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r}

data("Constipation")
summary <- generate_summary_string(data.obj)
summary

```

```{r}
#	out <- tableby(as.formula(paste0(grp.name, ' ~ ',  paste(colnames(data.obj$meta.dat)[summary.var.ind], collapse=' + '))), data=data.obj$meta.dat)
  #	sink('SampleCharacteristics.txt')
  #	summary(out, text=TRUE)
  #	sink()
  
  #	if (!is.null(adj.name)) {
  #		tab <- tableby(as.formula(paste0(grp.name, ' ~ ',  paste(adj.name, collapse='+'))), data=data.obj$meta.dat)
  #		save(tab, file='SummaryStat.RData')
  #	}
  
  
  cat("---Calculating sequence statistics  ...\n")
  perform_sequence_stat_analysis(data.obj, grp.name)
  
  
  cat("---Generate taxnomical profiles  ...\n")
  generate_taxa_heatmap(data.obj, meta.info=cluster.meta.info, taxa.levels = c('Phylum', 'Family', 'Genus'), prev=prev, minp=minp, ann = 'PhyFamGen')
  generate_stacked_barplot(data.obj, grp.name=grp.name.c, taxa.levels = c('Phylum', 'Family', 'Genus'),  order.auto = TRUE, order.taxa = TRUE, ann = 'PhyFamGen')

```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
